---
title: "Bicycle Sharing Activity"
author: "Feng Ding"
date: "10/22/2019"
output: 
    html_notebook:
    fig_height: 6
    fig_width: 10
---


# Set Up

### Clean up environment and load packages
```{r}
# clean up the RStudio environment 
rm(list = ls())
# load all packages here: `mosaic`, `tidyverse`, `lubridate`, and all others used

library(dplyr)
library(tidyverse)
library(ggplot2)


```

### Data Intake

The code chunk below loads the data for you, but you should study each line to understand what it's doing.

```{r}
### Load the station data set into our RStudio environment as described in the text
Stations <- mosaic::read.file("http://tiny.cc/dcf/DC-Stations.csv")
### Load the station data set into our RStudio environment as described in the text
# data_site <- "http://tiny.cc/dcf/2014-Q4-Trips-History-Data.rds"          # full data with 600k rows (uncomment to use)
data_site <- "http://tiny.cc/dcf/2014-Q4-Trips-History-Data-Small.rds"    # small data with 10k rows 
Trips <- readRDS(gzcon(url(data_site)))
### Backup code if you need to download the .rds file from the web and load a local version
# Trips <- readRDS("2014-Q4-Trips-History-Data-Small.rds")
# Trips <- readRDS("2014-Q4-Trips-History-Data.rds")
```



### Always inspect the data tables when you load them
```{r}
head(Stations)
head(Trips)
```




### Plot check-out times. (reproduce Figure 17.1: Use of shared bicycles over the three months in Q4.)
```{r}

```




# Section: How Long?

Make box & whisker plot showing the distribution of rental duration by client type.  As instructed in the text, make sure you either configure your scale or use a filter to suppress outliers from dictating the axis range.
```{r}

```



# Section: When are bikes used?

